---
title: "01_Cohort_Description"
author: "Adam Dziorny"
date: '2022-10-04'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The purpose of this markdown is to report information on the cohort necessary to populate "Table 1" of our publication.

## Initialize

First we load the necessary packages:

```{r, warning=FALSE}
suppressPackageStartupMessages({
  
  # Data frame manipulation
  require(dplyr)
  
  # Graphics and output
  require(ggplot2)
  require(cowplot)
  
  # Tables
  require(knitr)
  require(kableExtra)
})
```

Ensure the environmental variables are specified:

```{r}
if (Sys.getenv('PICU_LAB_DATA_PATH') == '' |
    Sys.getenv('PICU_LAB_IMG_PATH') == '' |
    Sys.getenv('PICU_LAB_IN_FILE') == '')
  stop('Missing necessary environmental variables - see README.md')
```

## Data Input

Load data from the `DATA_PATH` with the associated `IN_FILE`, adding a file separator between them. This should result in loading two data frames: `cohort.df` and `labs.df`.

```{r}
load(
  file = file.path(
    Sys.getenv('PICU_LAB_DATA_PATH'),
    Sys.getenv('PICU_LAB_IN_FILE')
  )
)
```

## Cohort Counts

Display counts of the ICU admissions (by `ENC_KEY`), hospital encounters (by `HOSP_KEY`) and patients (by `PAT_KEY`) for this site:

```{r}
# ICU, hospital, and patient counts 
cat(sprintf('# Unique ICU encounters: %d\n', 
            length(unique(cohort.df$ENC_KEY))))

cat(sprintf('# unique Hospital encounters: %d\n',
            length(unique(cohort.df$HOSP_KEY))))

cat(sprintf('# unique Patients: %d\n',
            length(unique(cohort.df$PAT_KEY))))
```

Gender split. Note that these are distinct to each patient `PAT_KEY`, and so are taken as distinct to those keys first:

```{r}
cohort.df %>%
  dplyr::distinct(PAT_KEY, SEX) %>%
  dplyr::group_by(SEX) %>%
  dplyr::summarise(
    cnt = n(),
    perc = cnt / length(unique(cohort.df$PAT_KEY)) * 100.
  ) %>%
  knitr::kable(
    col.names = c('Sex', 'Count', '%'),
    digits = c(0,0,2)
  ) %>%
  kableExtra::kable_paper(c("hover", "striped"), full_width = F)
```

Age at admission in years (ensure maximum age is < 18 years):

```{r}
summary(cohort.df$AGE_ICU_IN / 365.25)

# QQ Plot
cohort.df %>%
  ggplot(aes(sample = AGE_ICU_IN)) +
  stat_qq() +
  theme_bw()

# Test for normality:
ks.test(cohort.df$AGE_ICU_IN, 'pnorm')
```

ICU length of stay (in days):

```{r}
summary(cohort.df$ICU_LOS / 24.)

# QQ Plot
cohort.df %>%
  ggplot(aes(sample = ICU_LOS)) +
  stat_qq() +
  theme_bw()

# Test for normality:
ks.test(cohort.df$ICU_LOS, 'pnorm')
```

Total ICU Days - round up from LOS, add together:

```{r}
sum(ceiling(cohort.df$ICU_LOS / 24.))
```

Hospital mortality (use the column `DISCH_DISP` which has standard values). Note that these are distinct to hospital encounters (`HOSP_KEY`), and so are first taken as the distinct value of those:

```{r}
cohort.df %>%
  dplyr::distinct(HOSP_KEY, DISCH_DISP) %>%
  dplyr::group_by(DISCH_DISP) %>%
  dplyr::summarise(
    cnt = n(),
    perc = cnt / nrow(cohort.df) * 100.
  ) %>%
  knitr::kable(
    col.names = c('Discharge Disposition', 'Count', '%'),
    digits = c(0,0,2)
  ) %>%
  kableExtra::kable_paper(c("hover", "striped"), full_width = F)
```

