---
title: "10_Combine_Figures"
author: "Adam Dziorny"
date: '2022-10-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The purpose of this markdown is to generate combined (CHOP + URMC) figures for publication. 

## Initialize

First we load the necessary packages:

```{r, warning=FALSE}
suppressPackageStartupMessages({
  
  # Data frame manipulation
  require(dplyr)
  
  # Graphics and output
  require(ggplot2)
  require(cowplot)

  # Tables
  require(knitr)
  require(kableExtra)
  
  # Error grid point allocation
  require(ptinpoly)

})
```

Ensure the environmental variables are specified:

```{r}
if (Sys.getenv('PICU_LAB_DATA_PATH') == '' |
    Sys.getenv('PICU_LAB_IMG_PATH') == '' |
    Sys.getenv('PICU_LAB_IN_FILE') == '' |
    Sys.getenv('PICU_LAB_SITE_NAME') == '')
  stop('Missing necessary environmental variables - see README.md')
```

Specify the run date of the source data files - this will be the same run date for the output images:

```{r}
run.date <- '2022-10-05'
```


#### Image Parameters

```{r}
ext <- '.tiff'

dpi <- 600
```

### Variable Extraction Functions

Here we define several helper functions for extracting variabes out of RData files. These are useful to pull specific variables from rData files into the `.GlobalEnv` without loading the entire rData file. 

```{r}
#'
#' @title Make File Name
#' 
#' @description Helper function to make the file name from site, file, run.date
#' 
.makeFileName <- function (site, file, run.date) {
  
  return(
    file.path(
      Sys.getenv('PICU_LAB_DATA_PATH'),
      paste0(site, '_', file, '_', run.date, '.rData')
    )
  )
}

#'
#' @title List Vars
#' 
#' @description Lists the variables within an rData file
#' 
#' @param site The name of the site for extraction (e.g. `URMC` or `CHOP`)
#' @param file The rData file name (without the `<site>` or `<date>` parts)
#' @param run.date The run.date string
#' @param attach If TRUE, attaches to the file [Default]
#' @param detach If TRUE, detaches the file after extraction [Default]
#'
listVars <- function (site, file, run.date, attach = T, detach = T) {

  file.name <- .makeFileName(site,file,run.date)
  
  if (attach)
    attach(file.name)
  
  pos <- which(search() == paste0('file:', file.name))
  

  print(ls(pos = pos))
  
  if (detach)
    detach(pos = pos)
}

#'
#' @title Extract Var
#' 
#' @description Extracts a variable from an rData file to the Global Env 
#' 
#' @param old.var The variable name in the rData file (not character string)
#' @param new.var.name The character string of the new variable name to be 
#'     stored in the Global Env
#' @param site The name of the site for extraction (e.g. `URMC` or `CHOP`)
#' @param file The rData file name (without the `<site>` or `<date>` parts)
#' @param run.date The run.date string
#' @param attach If TRUE, attaches to the file [Default]
#' @param detach If TRUE, detaches the file after extraction [Default]
#'
extractVar <- function (old.var, new.var.name, site, file, run.date,
                        attach = T, detach = T) {
  
  file.name <- .makeFileName(site,file,run.date)
  
  if (attach)
    attach(file.name)
  
  pos <- which(search() == paste0('file:', file.name))
  
  assign(
    x = new.var.name,
    value = old.var,
    envir = .GlobalEnv
  )
  
  if (detach)
    detach(pos = pos)
}
```

To demonstrate how these work, we display the variables within the `thresholds_CBC-BG` file from `CHOP`, extract the `p` plot variable into the variable name `My_Var_Name`, display the plot, and remove it. 

```{r}
listVars('CHOP', 'thresholds_CBC-BG', run.date, detach = F)

extractVar(p, 'My_Var_Name', 'CHOP', 'thresholds_CBC-BG', run.date, attach = F)

print(My_Var_Name)

rm(My_Var_Name)
```

## Figure 1

Figure 1 is a six-panel figure, consisting of the three Bland-Altman figures across the top (CHOP BG, URMC BG, CHOP POC) followed by the three Error Grids across the bottom (same order - CHOP BG, URMC BG, CHOP POC). The B-A figures are stored in `pri_cbc_bg_analytic` and the error grids are stored in `pri_cbc_bg_clinical`.

First we view the variables to determine the BA plots (set to EVAL=FALSE since we don't need to do this each time):

```{r, eval=FALSE}
listVars('CHOP', 'pri_cbc_bg_analytic', run.date)
```

The variable of interest is `ba.all`. Here we load them from the respective files:

```{r}
extractVar(ba.all, 'p.CHOP.BA.BG', 'CHOP', 'pri_cbc_bg_analytic', run.date)

extractVar(ba.all, 'p.URMC.BA.BG', 'URMC', 'pri_cbc_bg_analytic', run.date)

extractVar(ba.all, 'p.CHOP.BA.POC', 'CHOP', 'pri_cbc_istat_analytic', run.date)
```

Now we view the variables to determine the Error_Grid plots (again set to EVAL=FALSE since we don't need to do this each time):

```{r, eval=FALSE}
listVars('CHOP', 'pri_cbc_bg_clinical', run.date)

listVars('CHOP', 'pri_cbc_istat_clinical', run.date)
```

The variable of interest is `error.grid.cbc.bg`. Here we load them from the respective files:

```{r}
extractVar(error.grid.cbc.bg, 'p.CHOP.EG.BG', 'CHOP', 'pri_cbc_bg_clinical', run.date)

extractVar(error.grid.cbc.bg, 'p.URMC.EG.BG', 'URMC', 'pri_cbc_bg_clinical', run.date)

extractVar(error.grid, 'p.CHOP.EG.POC', 'CHOP', 'pri_cbc_istat_clinical', run.date)
```

Generate the figure:

```{r}
Figure_1 <- 
  cowplot::plot_grid(
    p.CHOP.BA.BG$plot +
      ggtitle('CBC-BG (CHOP)') +
      xlab('Average Hgb') +
      ylab('Bias [CBC - BG Hgb]') +
      theme(
        title = element_text(size = 11),
        axis.title = element_text(size = 9)
      ),
    p.URMC.BA.BG$plot +
      ggtitle('CBC-BG (GCH)') +
      xlab('Average Hgb') +
      ylab('Bias [CBC - BG Hgb]') +
      theme(
        title = element_text(size = 11),
        axis.title = element_text(size = 9)
      ),
    p.CHOP.BA.POC$plot +
      ggtitle('CBC-POC') +
      xlab('Average Hgb') +
      ylab('Bias [CBC - POC Hgb]') +
      theme(
        title = element_text(size = 11),
        axis.title = element_text(size = 9)
      ),
    p.CHOP.EG.BG + 
      ggtitle('CBC-BG (CHOP)') +
      xlab('CBC Hgb (g/dL)') +
      ylab('BG Hgb (g/dL)') +
      theme(
        title = element_text(size = 11),
        axis.title = element_text(size = 9)
      ),
    p.URMC.EG.BG + 
      ggtitle('CBC-BG (GCH)') +
      xlab('CBC Hgb (g/dL)') +
      ylab('BG Hgb (g/dL)') +
      theme(
        title = element_text(size = 11),
        axis.title = element_text(size = 9)
      ),
    p.CHOP.EG.POC + 
      ggtitle('CBC-POC') +
      xlab('CBC Hgb (g/dL)') +
      ylab('POC Hgb (g/dL)') +
      theme(
        title = element_text(size = 11),
        axis.title = element_text(size = 9)
      ),
    labels = tolower(LETTERS[1:6]), 
    ncol = 3, nrow = 2)

print(Figure_1)

# Export 
ggplot2::ggsave(
  filename = file.path(
    Sys.getenv('PICU_LAB_IMG_PATH'),
    paste0('Figure-1_', run.date, ext)
  ),
  plot = Figure_1,
  width = 8, height = 6, units = 'in', dpi = dpi)
```

```{r, echo=FALSE}
rm(p.CHOP.BA.BG, p.URMC.BA.BG, p.CHOP.BA.POC)
rm(p.CHOP.EG.BG, p.URMC.EG.BG, p.CHOP.EG.POC)
rm(Figure_1)
```

### Supp Figure 1 

Supplemental figure 1 is a three-panel (vertical) figure of Hgb distributions. These data are stored in the `analytic` files:

```{r, eval=FALSE}
listVars('CHOP', 'pri_cbc_bg_analytic', run.date)
```

The variable of interest is `paired.res`:

```{r}
extractVar(paired.res, 'CHOP.dist.BG', 'CHOP', 'pri_cbc_bg_analytic', run.date)

extractVar(paired.res, 'URMC.dist.BG', 'URMC', 'pri_cbc_bg_analytic', run.date)

extractVar(paired.res, 'CHOP.dist.POC', 'CHOP', 'pri_cbc_istat_analytic', run.date)
```

Now create the figure:

```{r}
Supp_Figure_1 <- 
  cowplot::plot_grid(
    CHOP.dist.BG$density.p +
      coord_cartesian(xlim = c(4,22)) +
      ggtitle('CBC-BG (CHOP)') +
      theme(
        legend.position = c(0.85, 0.7)
      ),
    URMC.dist.BG$density.p + 
      coord_cartesian(xlim = c(4,22)) +
      ggtitle('CBC-BG (GCH)') +
      theme(
        legend.position = 'none'
      ),
    CHOP.dist.POC$density.p + 
      coord_cartesian(xlim = c(4,22)) +    
      ggtitle('CBC-POC') +
      theme(
        legend.position = 'none'
      ), 
    labels = tolower(LETTERS[1:3]), 
    ncol = 1, nrow = 3)

Supp_Figure_1

# Export 
ggplot2::ggsave(
  filename = file.path(
    Sys.getenv('PICU_LAB_IMG_PATH'),
    paste0('Supp-Figure-1_', run.date, ext)
  ),
  plot = Supp_Figure_1,
  width = 6, height = 7, units = 'in', dpi = dpi)
```

```{r, echo=FALSE}
rm(CHOP.dist.BG, CHOP.dist.POC, URMC.dist.BG)
rm(Supp_Figure_1)
```

### Supp Figure 2

Supplemental Figure 2 is a two-panel "Time To Result" plot. These are also found in `analytic` files.

```{r, eval=FALSE}
listVars('CHOP', 'pri_cbc_bg_analytic', run.date)
```

The variable of interest is `TTR.p`.

```{r}
extractVar(TTR.p, 'CHOP.TTR.BG', 'CHOP', 'pri_cbc_bg_analytic', run.date)

extractVar(TTR.p, 'URMC.TTR.BG', 'URMC', 'pri_cbc_bg_analytic', run.date)
```

And create the figure:

```{r}
Supp_Figure_2 <- 
  cowplot::plot_grid(
    CHOP.TTR.BG$plot + 
      ggtitle('CBC-BG (CHOP)') +
      theme(
        legend.position = c(0.8, 0.7)
      ),
    URMC.TTR.BG$plot + 
      ggtitle('CBC-BG (GCH)') +
      theme(
        legend.position = 'none'
      ),
    labels = tolower(LETTERS[1:2]), 
    ncol = 1, nrow = 2)

Supp_Figure_2

# Export 
ggplot2::ggsave(
  filename = file.path(
    Sys.getenv('PICU_LAB_IMG_PATH'),
    paste0('Supp-Figure-2_', run.date, ext)
  ),  
  plot = Supp_Figure_2,
  width = 7, height = 7, units = 'in', dpi = dpi)
```

```{r, echo=FALSE}
rm(CHOP.TTR.BG, URMC.TTR.BG)
rm(Supp_Figure_2)
```

### NNM Figure

The NNM figure is created from a manually-entered data frame of values, because we do not save the NNM (see ~ line 935 in `03_Clinical_Accuracy.Rmd`).

```{r}
nnm.vals <-
  rbind(
    data.frame(
      fn = 882, tn = 76768, cutoff = 7,
      site = 'CHOP', src = 'BG'),
    data.frame(
      fn = 445, tn = 76288, cutoff = 7.5,
      site = 'CHOP', src = 'BG'),
    data.frame(
      fn = 285, tn = 74877, cutoff = 8.0,
      site = 'CHOP', src = 'BG'),
    data.frame(
      fn = 210, tn = 72307, cutoff = 8.5,
      site = 'CHOP', src = 'BG'),
    data.frame(
      fn = 161, tn = 68535, cutoff = 9,
      site = 'CHOP', src = 'BG'),
    data.frame(
      fn = 51, tn = 4019, cutoff = 7,
      site = 'CHOP', src = 'POC'),
    data.frame(
      fn = 40, tn = 3959, cutoff = 7.5,
      site = 'CHOP', src = 'POC'),
    data.frame(
      fn = 19, tn = 3757, cutoff = 8,
      site = 'CHOP', src = 'POC'),
    data.frame(
      fn = 16, tn = 3633, cutoff = 8.5,
      site = 'CHOP', src = 'POC'),
    data.frame(
      fn = 9, tn = 3361, cutoff = 9,
      site = 'CHOP', src = 'POC'),
    data.frame(
      fn = 224, tn = 18389, cutoff = 7,
      site = 'GCH', src = 'BG'),
    data.frame(
      fn = 84, tn = 18206, cutoff = 7.5,
      site = 'GCH', src = 'BG'),
    data.frame(
      fn = 42, tn = 17700, cutoff = 8,
      site = 'GCH', src = 'BG'),
    data.frame(
      fn = 26, tn = 16794, cutoff = 8.5,
      site = 'GCH', src = 'BG'),
    data.frame(
      fn = 15, tn = 15604, cutoff = 9,
      site = 'GCH', src = 'BG'),
    stringsAsFactors = F)
```

Combine the CHOP and URMC BG values into a combo column:

```{r}
nnm.vals.added <- nnm.vals

for (cut in unique(nnm.vals$cutoff)) {
  nnm.vals.added <-
    rbind(
      nnm.vals.added,
      data.frame(
        fn = nnm.vals$fn[nnm.vals$src == 'BG' & nnm.vals$site == 'CHOP' & 
                           nnm.vals$cutoff == cut] +
          nnm.vals$fn[nnm.vals$src == 'BG' & nnm.vals$site == 'GCH' & 
                        nnm.vals$cutoff == cut],
        tn = nnm.vals$tn[nnm.vals$src == 'BG' & nnm.vals$site == 'CHOP' & 
                           nnm.vals$cutoff == cut] +
          nnm.vals$tn[nnm.vals$src == 'BG' & nnm.vals$site == 'GCH' & 
                           nnm.vals$cutoff == cut],
        cutoff = cut,
        src = 'BG',
        site = 'Combined'
      ),
      stringsAsFactors = F
    )
}

nnm.vals.added <-
  nnm.vals.added %>%
  dplyr::mutate(
    false_or = fn / (tn + fn),
    nnm = 1. / false_or,
    site = factor(site),
    src = factor(src)
  )
```

Create the plot and save out:

```{r}
nnm.fig <-
  nnm.vals.added %>%
  dplyr::filter(src == 'BG') %>%
  ggplot() +
  geom_point(aes(x = cutoff, y = nnm, color = site), size = 3) +
  geom_line(aes(x = cutoff, y = nnm, color = site), size = 1.5) +
  xlab('BG Cutoff (g/dL)') +
  ylab('Number Needed to Miss') +
  labs(color = 'Site') +
  scale_color_brewer(palette = 'Set2') +
  theme_bw() +
  theme(
    legend.position = c(0.2, 0.7)
  )

nnm.fig

ggplot2::ggsave(
  filename = file.path(
    Sys.getenv('PICU_LAB_IMG_PATH'),
    paste0('NNM_Figure_', run.date, ext)
  ), 
  plot = nnm.fig,
  width = 6, height = 4, units = 'in', dpi = dpi
)
```

```{r, echo=FALSE}
rm(nnm.vals, nnm.vals.added, cut)
rm(nnm.fig)
```






